Intelligent Reflecting Surface-Aided SWIPT: Joint Waveform, Active and Passive Beamforming Design

### 2021-03-05 main.tex
:pencil: Fix multisine amplitude
:pencil: Update notation

		\begin{subsection}{Low-Complexity Adaptive Design}
			\begin{subsubsection}{Waveform and Active Beamforming}
				The optimal resource allocation for WIT corresponds to the Water-Filling (WF) strategy that assigns the amplitude of modulated tone $n$ by
				\begin{equation}
					s_{\mathrm{I}, n} = \sqrt{\left(\mu - \frac{\sigma_n}{P \lVert{\boldsymbol{h}_n}\rVert^2}\right)^+}
				\end{equation}
				where $\mu$ is chosen to satisfy the power constraint $\lVert{\boldsymbol{s}_I}\rVert^2 / 2 \le P$. The closed-form solution can be obtained by iterative power allocation and the details are omitted here. On the other hand, the Scaled Matched Filter (SMF) was proposed in \cite{Clerckx2017} as a suboptimal resource allocation scheme for WPT. It involves no modulated waveform and assigns the amplitude of sinewave $n$ by
				\begin{equation}
					s_{\mathrm{P}, n} = \sqrt{\frac{2 P}{\sum_{n=1}^N \lVert{\boldsymbol{h}_n \rVert^{2 \beta}}}}\lVert{\boldsymbol{h}_n}\rVert^\beta
				\end{equation}
				where the only design variable $\beta \ge 1$ scales the matched filter to exploit the rectifier nonlinearity. $\beta = 1$ corresponds to a standard matched filter where the amplitude of sinewave $n$ is linearly proportional to the equivalent channel strength $\lVert{\boldsymbol{h}_n}\rVert$, while $\beta > 1$ further elevates the strong subchannels and suppresses the weak ones. The advantage of SMF has been experimentally demonstrated in a practical WPT system with channel acquisition \cite{Kim2017}.

				To facilitate practical SWIPT implementation, we provide two low-complexity adaptive design by combining WF and SMF under TS and PS setups.	Specifically, the low-complexity TS scheme divides each time slot into dedicated data session with proportion $1 - \eta$ and dedicated energy session with proportion $\eta$, then performs WF and SMF respectively. Varying $\eta$ from \num{0} to \num{1} corresponds to a R-E line from WIT point to WPT point. In contrast, the low-complexity PS scheme involves the design of splitting ratio $\rho$ as well as a superposed waveform, where the proportion of WF and SMF are controlled by a balancing ratio $\delta$ as
				\begin{align}
					s_{\mathrm{I}, n} &= \sqrt{(1 - \delta)\left(\mu - \frac{\sigma_n}{P \lVert{\boldsymbol{h}_n}\rVert^2}\right)^+} \\
					s_{\mathrm{P}, n} &= \sqrt{\frac{2 \delta P}{\sum_{n=1}^N \lVert{\boldsymbol{h}_n \rVert^{2 \beta}}}}\lVert{\boldsymbol{h}_n}\rVert^\beta
				\end{align}
				That is to say, the suboptimal TS scheme only need to design $\beta$ while the suboptimal PS scheme should also consider $\rho$ and $\delta$ for different R-E tradeoff.
			\end{subsubsection}
		\end{subsection}
	\end{section}

>>>>

		\begin{subsection}{Low-Complexity Adaptive Design}
			\begin{subsubsection}{Waveform and Active Beamforming}
				The optimal resource allocation for WIT corresponds to the Water-Filling (WF) strategy that assigns the amplitude of modulated tone $n$ by
				\begin{equation}
					s_{\mathrm{I}, n} = \sqrt{2\left(\mu - \frac{\sigma_n}{P \lVert{\boldsymbol{h}_n}\rVert^2}\right)^+}
				\end{equation}
				where $\mu$ is chosen to satisfy the power constraint $\lVert{\boldsymbol{s}_I}\rVert^2 / 2 \le P$. The closed-form solution can be obtained by iterative power allocation and the details are omitted here. On the other hand, the Scaled Matched Filter (SMF) was proposed in \cite{Clerckx2017} as a suboptimal resource allocation scheme for WPT. It involves no modulated waveform and assigns the amplitude of sinewave $n$ by
				\begin{equation}
					s_{\mathrm{P}, n} = \sqrt{\frac{2 P}{\sum_{n=1}^N \lVert{\boldsymbol{h}_n \rVert^{2 \alpha}}}}\lVert{\boldsymbol{h}_n}\rVert^\alpha
				\end{equation}
				where the only design variable $\alpha \ge 1$ scales the matched filter to exploit the rectifier nonlinearity. $\alpha = 1$ corresponds to a standard matched filter where the amplitude of sinewave $n$ is linearly proportional to the equivalent channel strength $\lVert{\boldsymbol{h}_n}\rVert$, while $\alpha > 1$ further elevates the strong subchannels and suppresses the weak ones. The advantage of SMF has been experimentally demonstrated in a practical WPT system with channel acquisition \cite{Kim2017}.

				To facilitate practical SWIPT implementation, we provide two low-complexity adaptive design by combining WF and SMF under TS and PS setups.	Specifically, the low-complexity TS scheme divides each time slot into dedicated data session with proportion $1 - \eta$ and dedicated energy session with proportion $\eta$, then performs WF and SMF respectively. Varying $\eta$ from \num{0} to \num{1} corresponds to a R-E line from WIT point to WPT point. In contrast, the low-complexity PS scheme involves the design of splitting ratio $\rho$ as well as a superposed waveform, where the proportion of WF and SMF are controlled by a balancing ratio $\delta$ as
				\begin{align}
					s_{\mathrm{I}, n} &= \sqrt{2(1 - \delta)\left(\mu - \frac{\sigma_n}{P \lVert{\boldsymbol{h}_n}\rVert^2}\right)^+} \\
					s_{\mathrm{P}, n} &= \sqrt{\frac{2 \delta P}{\sum_{n=1}^N \lVert{\boldsymbol{h}_n \rVert^{2 \alpha}}}}\lVert{\boldsymbol{h}_n}\rVert^\alpha
				\end{align}
				That is to say, the suboptimal TS scheme only need to design $\alpha$ while the suboptimal PS scheme should also consider $\rho$ and $\delta$ for different R-E tradeoff.
			\end{subsubsection}
		\end{subsection}
	\end{section}
